---
title: "homework1"
author: "Bernardo Magalhaes, Adhish Luitel, Ji Heon Shim"
date: "`r format(Sys.Date())`" 
always_allow_html: true
output:
    md_document:
    variant: markdown_github
---
#ECO 395M: Exercise 2

Bernardo Arreal Magalhaes - UTEID ba25727

Adhish Luitel - UTEID al49674

Ji Heon Shim - UTEID js93996

## Exercise 2.2
```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dummies)
library(margins)
library(dplyr)
library(kableExtra)
library(sjPlot)
library(mosaic)

brca = read.csv(url("https://raw.githubusercontent.com/bmagalhaes/ECO395M-HW2/master/brca.csv"))
```
This exercise is based on a dataset consisted of 987 screening mammograms administered at a hospital in Seattle, Washington. The goal of the analysis is to evaluate the performance of five different radiologists considering several risk factors.

First, we analyzed the raw data to verify whether each radiologist has a different recall rate or not, and compare precision and error rates. We can observe that, even though radiologist89 has a higher probability of recalling patients, his Type II error rate (not recalling patients that actually have cancer) doesn't substantially differ from radiologist95 and radiologist34, who have the lowest recall rates.

```{r 2.2.1, echo=FALSE}
recall_rate = brca %>%
  group_by(radiologist)  %>%
  summarize(A.recallrate = length(which(recall == 1)) / (length(which(recall == 1))
            + length(which(recall == 0))))

recall_rate = recall_rate[order(-recall_rate$A.recallrate),c(1,2)]
recall_rate = mutate(recall_rate, n = row_number())

cancer_rate = brca %>%
  group_by(radiologist)  %>%
  summarize(B.cancerrate = length(which(recall == 1 & cancer == 1)) / (length(which(recall == 1 & 
            cancer == 1)) + length(which(recall == 1 & cancer == 0))))

error_rate = brca %>%
  group_by(radiologist)  %>%
  summarize(C.error = length(which(recall == 0 & cancer == 1)) / (length(which(recall == 0 & 
            cancer == 1)) + length(which(recall == 0 & cancer == 0))))

radiologist = left_join(recall_rate, cancer_rate, by = "radiologist")
radiologist = left_join(radiologist, error_rate, by = "radiologist")

radiologist_long = radiologist %>%
  gather("Stat", "Value", -radiologist, -n)
radiologist_long = mutate(radiologist_long, Value = Value*100)

radiologist_89 = radiologist_long[which(radiologist_long$n==1), ]

ggplot(data = radiologist_long) + 
  geom_bar(mapping = aes(x=reorder(radiologist, -n), y=Value),
           stat='identity', position ='dodge', fill="lightgray", color="black", alpha=.6, width=.5) + 
  facet_wrap(~Stat) + 
  coord_flip() +
  labs(y="Observed rate (in percentage)", x = "") +
  geom_hline(data= radiologist_89, aes(yintercept=Value), color="red" , linetype = "dashed") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major.y = element_blank(), panel.grid.minor.y = element_blank()) 
```

However, since each radiologist read the mammograms of a different set of patients, this difference could be explained by the fact that some radiologists might have seen patients whose clinical situation required the patient to be recalled for further examination.

In order to analyse if, holding patient risk factors equal, some radiologists are more clinically conservative than others in recalling patients, we built two classification models:

```{r 2.2.2, echo=TRUE}
model1 = recall ~ radiologist + age + history + symptoms + menopause + density
model2 = recall ~ (age + history + symptoms + menopause + density) * radiologist
```

The table below shows the Average Marginal Effect (AME) for each radiologist in the two models. We can see that, when using Model 1, radiologist89 is the most conservative - holding patient risk factors equal, the probability of being recalled increases by 5.71 percentage points when radiologist89 is the one reading the mammogram compared to the baseline radiologist13.

When allowing for interactions between radiologist and each control variable as in Model 2, radiologist89 is still the most conservative - holding patient risk factors equal, the probability of being recalled increases by 17.48 percentage points when radiologist89 is the one reading the mammogram compared to the baseline radiologist13.

```{r 2.2.3, echo=FALSE}
brca2 = brca
brca2$radiologist_raw = brca2$radiologist
brca2$radiologist = str_replace(brca2$radiologist, "radiologist","")
brca2$age = str_replace(brca2$age, "age","")
brca2$menopause = str_replace(brca2$menopause, "meno","")
brca2$density = str_replace(brca2$density, "density","")

brca_new = dummy.data.frame(brca2, names = c("radiologist", "age","menopause", "density") , sep = ".")
brca_new = subset(brca_new, select = -c(radiologist.13, age.4049,menopause.postHT, density.1))

model_1 = glm(recall ~ . - cancer, data=brca_new, family=binomial)
ame_11 = summary(margins(model_1, variables = list("radiologist.34", "radiologist.66", "radiologist.89", "radiologist.95"), vce = "bootstrap"))

model_2 = glm(recall ~ (history + symptoms + age.5059 + age.6069 + age.70plus + menopause.postNoHT
              + menopause.postunknown + menopause.pre + density.2 + density.3 + density.4)*(radiologist.34
              + radiologist.66 + radiologist.89 + radiologist.95), data=brca_new, family=binomial)
ame_21 = summary(margins(model_2, variables = list("radiologist.34", "radiologist.66", "radiologist.89", "radiologist.95"), vce = "bootstrap"))

ame_11 = select(ame_11,-c(4:7))
ame_21 = select(ame_21,-c(4:7))

ame = left_join(ame_11, ame_21, by = "factor")
colnames(ame) <- c("","AME","se","AME","se")

kable(ame) %>%
  kable_styling("striped") %>%
  add_header_above(c(" " = 1, "Model 1" = 2, "Model 2" = 2))
```

Finally, in order to estimate how each radiologist would perform when facing the same set of patients, we used a bootstrap to randomly split the original dataset in a training dataset containing 80% of the observations and a testing a dataset containing 20% of the observations, repeating the proccess 100 times. In each repetition, we fitted both models using the train dataset, and compared each model's predictions when all radiologists, in a hypothetical scenario, analyze the entire test dataset. 

We computed average probability of recall per repetition, and calculated the average of the 100 samples to mitigate the effect of randomization. For both models, radiologist89 has the highest probability of recall, followed by radiologist66, radiologist13, radiologist95 and radiologist 34.

```{r 2.2.4, echo=FALSE}
n = nrow(brca_new)

boot1 = do(100)*{
  
  # re-split into train and test cases
  n_train = round(0.8*n)  # round to nearest integer
  n_test = n - n_train
  train_cases = sample.int(n, n_train, replace=FALSE)
  test_cases = setdiff(1:n, train_cases)
  brca_train = brca_new[train_cases,]
  brca_test = brca_new[test_cases,]
  brca_test = brca_test[rep(seq_len(nrow(brca_test)), 5),]
  brca_test =  brca_test %>%
    mutate(n = row_number()) %>%
    mutate(radiologist.34 = 0) %>%
    mutate(radiologist.66 = 0) %>%
    mutate(radiologist.89 = 0) %>%
    mutate(radiologist.95 = 0)
  brca_test =  brca_test %>%
    mutate(radiologist.34 = 0) %>%
    mutate(radiologist.66 = 0) %>%
    mutate(radiologist.89 = 0) %>%
    mutate(radiologist.95 = 0)
  brca_test = brca_test %>%
    mutate(radiologist.34 = ifelse(radiologist_raw == "radiologist34", 1, 0)) %>%
    mutate(radiologist.66 = ifelse(radiologist_raw == "radiologist66", 1, 0)) %>%
    mutate(radiologist.89 = ifelse(radiologist_raw == "radiologist89", 1, 0)) %>%
    mutate(radiologist.95 = ifelse(radiologist_raw == "radiologist95", 1, 0))
  
  # fit to this training set
  glm_1 = glm(recall ~ . - cancer, data=brca_train, family=binomial)
  glm_2 = glm(recall ~ (history + symptoms + age.5059 + age.6069 + age.70plus + menopause.postNoHT
                        + menopause.postunknown + menopause.pre + density.2 + density.3 + density.4)*(radiologist.34
                        + radiologist.66 + radiologist.89 + radiologist.95), data=brca_train, family=binomial)
  
  # predict on this testing set
  yhat_test1 = predict(glm_1, brca_test, type="response")
  yhat_test2 = predict(glm_2, brca_test, type="response")

  brca_test$pred1 = yhat_test1
  brca_test$pred2 = yhat_test2
  recalls_1 = brca_test %>%
    group_by(radiologist_raw)  %>%
    summarize(recalls = mean(pred1))
  recalls_2 = brca_test %>%
    group_by(radiologist_raw)  %>%
    summarize(recalls = mean(pred2))
  recalls_t = rbind(recalls_1, recalls_2)
  recalls = as.data.frame(t(recalls_t))
  recalls = recalls[-1, ]
  colnames(recalls) <- c("M1_radiologist.13", "M1_radiologist.34", "M1_radiologist.66", 
                         "M1_radiologist.89", "M1_radiologist.95", "M2_radiologist.13",
                         "M2_radiologist.34", "M2_radiologist.66", 
                         "M2_radiologist.89", "M2_radiologist.95")
  recalls
  }

boot1[, c(1:10)] = sapply(boot1[, c(1:10)], as.numeric)

radiologist = c("radiologist.13", "radiologist.34", "radiologist.66", "radiologist.89", "radiologist.95")
Model_1 = c(mean(boot1$M1_radiologist.13), mean(boot1$M1_radiologist.34), mean(boot1$M1_radiologist.66),
       mean(boot1$M1_radiologist.89), mean(boot1$M1_radiologist.95))
Model_2 = c(mean(boot1$M2_radiologist.13), mean(boot1$M2_radiologist.34), mean(boot1$M2_radiologist.66),
       mean(boot1$M2_radiologist.89), mean(boot1$M2_radiologist.95))
a = data.frame(radiologist, Model_1,Model_2)

kable(a) %>%
  kable_styling("striped") %>%
  add_header_above(c(" " = 1, "(Out of sample) Average recall probability" = 2))
```