---
title: "homework2"
author: "Bernardo Magalhaes, Adhish Luitel, Ji Heon Shim"
date: "`r format(Sys.Date())`" 
always_allow_html: true
output:
    md_document:
    variant: markdown_github
---
#ECO 395M: Exercise 2

Bernardo Arreal Magalhaes - UTEID ba25727

Adhish Luitel - UTEID al49674

Ji Heon Shim - UTEID js93996

## Exercise 2.1
```{r setup1, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dummies)
library(margins)
library(dplyr)
library(kableExtra)
library(sjPlot)
library(mosaic)
library(FNN)
library(foreach)
data(SaratogaHouses)
```
In this exercise, we hand-build five models for price in order to find out the best one which outperforms the "medium" model that we considered in class.

```{r 2.1.1, echo= TRUE, warning = FALSE}
model1= price ~ lotSize + age + landValue + livingArea + pctCollege + bedrooms + fireplaces + bathrooms + heating + fuel + sewer + waterfront + newConstruction + centralAir 
model2= price~ lotSize + age + landValue + livingArea + pctCollege + bedrooms + fireplaces + bathrooms + heating + fuel + centralAir 
model3= price~ (lotSize + age + landValue + livingArea + pctCollege + bedrooms + fireplaces + bathrooms + heating + fuel + centralAir)^2 
model4= price~ lotSize + age +pctCollege * landValue + livingArea * (bedrooms + bathrooms) + fireplaces + heating + fuel + centralAir
model5= price~ lotSize + age + age2 + pctCollege * landValue + livingArea * (bedrooms + bathrooms) + fireplaces + heating + fuel + centralAir

model_medium = price ~ lotSize + age + livingArea + pctCollege + bedrooms + 
                 fireplaces + bathrooms + rooms + heating + fuel + centralAir

```

Here are the main features of our models.

Model 1 : include all main effects except roooms
(exclude rooms because of colinearity, rooms = bedrooms + batherooms)
Model 2: simplify model1 by reducing some variables(-sewer-waterfront-newConstruction)
Model 3: add all the interactions on model 2
Model 4: allow only some interactions on model 2
Model 5: a polynomial model by adding age^2 on model 4
Model_medium: baseline model with 11 main effects
             
```{r 2.1.2, echo=FALSE}
# make a new variable age2=(age)^2
SaratogaHouses <- mutate(SaratogaHouses, age2=(age)^2)

rmse = function(y, yhat) {
  sqrt( mean( (y - yhat)^2 ) )
}
```
In order to measure performances of each model, we run the Monte Carlo training-test split(train 80%, test 20%) for 100 times and calcaulate the average values of out-of-sample RMSE for each model.
And the best model turned out to be model 1 with the least out-of-sample RMSE value.

```{r 2.1.3, echo=FALSE}
rmse_check = do(100)*{# Split into training and testing sets
n = nrow(SaratogaHouses)
n_train = round(0.8*n)  # round to nearest integer
n_test = n - n_train
train_cases = sample.int(n, n_train, replace=FALSE)
test_cases = setdiff(1:n, train_cases)
saratoga_train = SaratogaHouses[train_cases,]
saratoga_test = SaratogaHouses[test_cases,]

#Hand-build some models and fit into training data

# model1: use all possible variables except rooms and age2 without interactions
# we get rid of "rooms" because of collinearity, rooms=bathrooms+bedrooms)
model1= lm(price ~ .-rooms-age2, data=saratoga_train)

# model2: simplify model1 by deleting some variables that look unimportant
# sewer(unimportant), waterfront, newConstruction(not enough samples with value of 1)
model2= lm(price~ .-rooms-sewer-waterfront-newConstruction-age2, data=saratoga_train)

# model3 : add all the interactions on model2
model3= lm(price~ (.-rooms-sewer-waterfront-newConstruction-age2)^2, data=saratoga_train)

# model4: allow only some interactions
model4= lm(price~ lotSize + age +pctCollege * landValue + livingArea * (bedrooms + bathrooms) + fireplaces + heating + fuel + centralAir, data=saratoga_train)

# add a new variables for polynomial regression on model4
# we added age^2 because it is likely that house price rapidly goes down as it becomes aged

model5= lm(price~ lotSize + age + age2 + pctCollege * landValue + livingArea * (bedrooms + bathrooms) + fireplaces + heating + fuel + centralAir, data=saratoga_train)

# our baseline model, medium
model_medium = lm(price ~ lotSize + age + livingArea + pctCollege + bedrooms + 
                 fireplaces + bathrooms + rooms + heating + fuel + centralAir, data=saratoga_train)

# Predictions out of sample
yhat_test1 = predict(model1, saratoga_test)
yhat_test2 = predict(model2, saratoga_test)
yhat_test3 = predict(model3, saratoga_test)
yhat_test4 = predict(model4, saratoga_test)
yhat_test5 = predict(model5, saratoga_test)
yhat_test_medium = predict(model_medium, saratoga_test)

c(rmse(saratoga_test$price, yhat_test1), rmse(saratoga_test$price, yhat_test2), rmse(saratoga_test$price, yhat_test3), rmse(saratoga_test$price, yhat_test4), rmse(saratoga_test$price, yhat_test5), rmse(saratoga_test$price, yhat_test_medium))}

rmse_result= data.frame('model1'= colMeans(rmse_check[1]), 'model2'=colMeans(rmse_check[2]), 'model3'=colMeans(rmse_check[3]), 'model4'=colMeans(rmse_check[4]), 'model5'=colMeans(rmse_check[5]), 'model_medium'=colMeans(rmse_check[6]))

rmse_result

```



